Interisland movements of woodland caribou in Newfoundland

### 2020-02-19 paper/manuscript.Rmd
sorry I didn't finish my comments on the last stage -___- I also: - streamlined intro/context - explained methods - added section on individual variation (classic Jack, tbh)

Caribou were introduced to Fogo Island (n = 26 animals between
1964–67) and Change Island (n = 5 animals in 1964) from the main
Island of Newfoundland as part of a series of translocations and introductions
throughout the province (Bergerud & Mercer 1989). While caribou populations are
in decline throughout Canada (Festa-Bianchet et al. 2011), as well as in
Newfoundland (Bastille-Rousseau et al. 2013), the Fogo Island herd has not
declined to the same extent and currently consists of approximately 300 animals
(Newfoundland and Labrador Wildlife Division, unpublished data). Since 2016 we
have been studying the Fogo Island caribou herd (Bonar et al. 2017; Bonar et al.
2018; Peignier et al. 2019). To date, we have fitted 29 adult female caribou
with GPS collars (1240g, GPS 4400M; Lotek Wireless Inc., Newmarket, Ontario,
Canada), which were programmed to collect relocation fixes every 2 hours (see
Bonar et al. 2018 for details). We used GPS locations from these individuals to investigate oceanic swimming events.

>>>>

Caribou were introduced to Fogo Island (n = 26 animals between
1964–67) and Change Island (n = 5 animals in 1964) from the main
Island of Newfoundland as part of a series of translocations and introductions
throughout the province (Bergerud & Mercer 1989). Since 2016 we
have been studying the Fogo Island caribou herd (Bonar et al. 2017; Bonar et al.
2018; Peignier et al. 2019). To date, we have fitted 29 adult female caribou
with GPS collars (1240g, GPS 4400M; Lotek Wireless Inc., Newmarket, Ontario,
Canada), which were programmed to collect relocation fixes every 2 hours (see
Bonar et al. 2018 for details). We used GPS locations from these individuals to investigate oceanic swimming events.
